---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(grant)
```

# Overview

Grant is an R package designed to provide a comprehensive exploration of grant opportunities in the United States. The package contains a dataset with detailed information about various grants, including categories, award ceilings, award floors, eligibility and application deadlines.



## Installation

You can install the development version of grant from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")

remotes::install_github("ETC5523-2024/assignment-4-packages-and-shiny-apps-sarah-liu17", subdir = "grant")
```

## Example

This is an example to explore the grants by category

```{r example}
summarize_grants_by_category(grant_opp)
```

To visualise the top funded grants by the desired number
```{r}
top_funded_grants(grant_opp, grant, 5)
```


## Shiny interactive app to explore the grants
```{r, eval = FALSE, echo=TRUE}
run_grant_app()
```

There are different options of interactive features inside the app, which allow
the users to first investigate about grant opportunities according to their 
expectations of eligibility, closing date and category. Users could then develop
a clear understanding of the award range they are applying for to meet their
capital needs by looking at the categories in the bar chart and the table for
specific grants. The top funded grants are included at last to provide an overall
picture of what areas are most invested by the government to secure users' fundings.
